Phylogenetic inference of contact network parameters with approximate Bayesian computation

### 2016-07-25 doc/defence/transtree2.tex
Final changes to defence presentation

\begin{frame}{Contact networks shape transmission trees}
  \vspace{-1cm}
  \begin{center}
    \begin{tikzpicture}
      [every node/.style = {inner sep=0pt},
       every path/.style = {->, >=stealth, very thick},
       label/.style = {anchor=south, color=white, inner sep=4pt},
       time/.style = {anchor=north west, inner sep=2pt}]
      \def\pht{1cm}
      \node (a) {\includegraphics[height=\pht]{stock/person}};
      \node at (a.south) [label] {\Large a};
      \node [below left=0.75 of a] (b) {\includegraphics[height=\pht]{stock/person}};
      \node at (b.south) [label] {\Large b};
      \node [below=0.75 of b] (e) {\includegraphics[height=\pht]{stock/person}};
      \node at (e.south) [label] {\Large e};
      \node [below right=0.75 of a] (c) {\includegraphics[height=\pht]{stock/person}};
      \node at (c.south) [label] {\Large c};
      \node [below=0.75 of c] (d) {\includegraphics[height=\pht]{stock/person}};
      \node at (d.south) [label] {\Large d};

      \fill [shade, opacity=0.2] (a.east) -- (c.north) -- (c.north west) -- (a.south east) -- cycle;
      \fill [shade, opacity=0.2] (a.west) -- (b.north) -- (b.north east) -- (a.south west) -- cycle;
      \fill [shade, opacity=0.2] (a.south) -- (a.south west) -- (e.north) -- (e.north east) -- cycle;
      \fill [shade, opacity=0.2] (b.south west) -- (b.south) -- (e.north) -- (e.north west) -- cycle;
      \fill [shade, opacity=0.2] ($(c.south) + (-8pt, 0)$) -- ++(16pt, 0) -- ($(d.north) + (8pt, 0)$) -- ++(-16pt, 0) -- cycle;
      \fill [shade, opacity=0.2] (b.east) -- (b.south east) -- (d.west) -- (d.north west) -- cycle;
      \uncover<2->{
      \draw [red] ($(a.west) + (0, -12pt)$) -- ($(b.north) + (8pt, 0)$);
      }
      \uncover<4->{
      \draw [blue] ($(a.east) + (0, -12pt)$) -- ($(c.north) + (-8pt, 0)$);
      }
      \uncover<6->{
      \draw [green!80!black] (c) -- (d);
      }

      \node (abcd) [above right=0 and 5cm of a] {\includegraphics[height=\pht]{stock/person}};
      \node at (abcd.south) [label] {\Large a};

      \uncover<2>{
      \node (b) at (abcd.east) [anchor=west] {\includegraphics[height=\pht]{stock/person}};
      \node at (b.south) [label] {\Large b};
      \draw [red] (abcd.south) to [bend right=75] (b.south);
      }

      \uncover<3->{
      \node (b) [below right=1 and 0.75 of abcd] {\includegraphics[height=\pht]{stock/person}};
      \node at (b.south) [label] {\Large b};
      \node (acd) [below left=1 and 0.5 of abcd] {\includegraphics[height=\pht]{stock/person}};
      \node at (acd.south) [label] {\Large a};
      \draw [red] (abcd) -- (b);
      \draw [-, dashed] (abcd) -- (acd);
      }

      \uncover<4>{
      \node (cd) at (acd.east) [anchor=west] {\includegraphics[height=\pht]{stock/person}};
      \node at (cd.south) [label] {\Large c};
      \draw [blue] (acd.south) to [bend right=75] (cd.south);
      }

      \uncover<5->{
      \node (cd) [below right=0.5 and 0.5 of acd] {\includegraphics[height=\pht]{stock/person}};
      \node at (cd.south) [label] {\Large c};
      \node (a) [below left=0.25 and 0.25 of acd] {\includegraphics[height=\pht]{stock/person}};
      \node at (a.south) [label] {\Large a};
      \draw [blue] (acd) -- (cd);
      \draw [-, dashed] (acd) -- (a);
      }

      \uncover<6>{
      \node (d) at (cd.east) [anchor=west] {\includegraphics[height=\pht]{stock/person}};
      \node at (d.south) [label] {\Large d};
      \draw [green] (cd.south) to [bend right=75] (d.south);
      }

      \uncover<7->{
      \node (c) [below left=0.25 and 0.25 of cd] {\includegraphics[height=\pht]{stock/person}};
      \node at (c.south) [label] {\Large c};
      \node (d) [below right=0.4 and 0.4 of cd] {\includegraphics[height=\pht]{stock/person}};
      \node at (d.south) [label] {\Large d};
      \draw [-, dashed] (cd) -- (c);
      \draw [green!80!black] (cd) -- (d);
      }

@@

    \end{tikzpicture}

  $\qquad$contact network \hfill transmission tree$\qquad$
  \end{center}
\end{frame}

>>>>

\begin{frame}{Transmission trees record the progress of an epidemic}
  \vspace{-1cm}
  \begin{center}
    \begin{tikzpicture}
      [every node/.style = {inner sep=0pt},
       every path/.style = {->, >=stealth, very thick},
       label/.style = {anchor=south, color=white, inner sep=4pt},
       time/.style = {anchor=north west, inner sep=2pt}]
      \def\pht{1cm}
      \node (abcd) {\includegraphics[height=\pht]{stock/person}};
      \node at (abcd.south) [label] {\Large a};

      \node (b) [below right=1 and 0.75 of abcd] {\includegraphics[height=\pht]{stock/person}};
      \node at (b.south) [label] {\Large b};
      \node (acd) [below left=1 and 0.5 of abcd] {\includegraphics[height=\pht]{stock/person}};
      \node at (acd.south) [label] {\Large a};
      \draw [red] (abcd) -- (b);
      \draw [-, dashed] (abcd) -- (acd);

      \node (cd) [below right=0.5 and 0.5 of acd] {\includegraphics[height=\pht]{stock/person}};
      \node at (cd.south) [label] {\Large c};
      \node (a) [below left=0.25 and 0.25 of acd] {\includegraphics[height=\pht]{stock/person}};
      \node at (a.south) [label] {\Large a};
      \draw [blue] (acd) -- (cd);
      \draw [-, dashed] (acd) -- (a);

      \node (c) [below left=0.25 and 0.25 of cd] {\includegraphics[height=\pht]{stock/person}};
      \node at (c.south) [label] {\Large c};
      \node (d) [below right=0.4 and 0.4 of cd] {\includegraphics[height=\pht]{stock/person}};
      \node at (d.south) [label] {\Large d};
      \draw [-, dashed] (cd) -- (c);
      \draw [green!80!black] (cd) -- (d);

@@

      \uncover<2->{
      \node (t) [above left=0 and 2 of acd, inner xsep=4pt] {transmission};
      \draw [thin] (t.east) -- (acd);
      }

      \uncover<3->{
      \node (t) [below left=0 and 1 of a, inner xsep=4pt] {sampling/removal};
      \draw [thin, shorten >=4pt] (t.east) -- (a);
      }

    \end{tikzpicture}
  \end{center}
\end{frame}
